Making Sequential Programs Deterministic

### 2019-04-04 experiments.tex
deflaker expts
Tweaks

All the flakiness that NonDex found was due to 7 methods in 3 classes. We enumerate all the methods corresponding to
each class in Figure~\ref{fig:flaky-sources}.
\begin{figure}
    \begin{tabular}{lll}
        \<Class> & : \<getDeclaredFields>, \<getDeclaredMethods>, \<getFields> \\
        \<DateFormatSymbols> & : \<getZoneStrings> \\
        \<HashMap> & : \<entrySet>, \<keySet>, \<values>
    \end{tabular}
\caption{Souces of flakiness in~\cite{nondex}.}
\label{fig:flaky-sources}
\end{figure}

We provide samples of the annotated source code from these benchmarks and the errors as reported by \TheDeterminismChecker 
in Figure~\ref{fig:nondex-source}.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.95\textwidth}
        \begin{verbatim}
    static public FieldAccess get (Class type) {
        @Det ArrayList<@Det Field> fields = new ArrayList<Field>();
        ...
        while (nextClass != Object.class) {
            @Det Field @Det[] declaredFields = nextClass.getDeclaredFields();
            ...
        }
    }
    [ERROR] FieldAccess.java:[102,87] 
    incompatible types in assignment.
    found   : @Det Field @OrderNonDet []
    required: @Det Field @Det []
        \end{verbatim}
        \caption{Annotated source code from reflectasm. \vspace{0.5cm}}
        \label{code-reflectasm}
    \end{subfigure}

@@

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. Ideally, we would have 
liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
in its repository.

>>>>

All the flakiness that NonDex found was due to 7 methods in 3 classes. We enumerate all the methods corresponding to
each class in \cref{fig:flaky-sources}.
\begin{figure}
    \begin{tabular}{lll}
        \<Class> & : \<getDeclaredFields>, \<getDeclaredMethods>, \<getFields> \\
        \<DateFormatSymbols> & : \<getZoneStrings> \\
        \<HashMap> & : \<entrySet>, \<keySet>, \<values>
    \end{tabular}
\caption{Souces of flakiness in~\cite{nondex}.}
\label{fig:flaky-sources}
\end{figure}

We provide samples of the annotated source code from these benchmarks and the errors as reported by \TheDeterminismChecker 
in \cref{fig:nondex-source}.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.95\textwidth}
        \begin{verbatim}
    static public FieldAccess get (Class type) {
        @Det ArrayList<@Det Field> fields = new ArrayList<Field>();
        ...
        while (nextClass != Object.class) {
            @Det Field @Det[] declaredFields = nextClass.getDeclaredFields();
            ...
        }
    }
    [ERROR] FieldAccess.java:[102,87] 
    incompatible types in assignment.
    found   : @Det Field @OrderNonDet []
    required: @Det Field @Det []
        \end{verbatim}
        \caption{Annotated source code from reflectasm. \vspace{0.5cm}}
        \label{code-reflectasm}
    \end{subfigure}

@@

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. Ideally, we would have 
liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
in its repository.
\todo{Deflaker works now. Tried on retrofit: only works where there is sufficient change in code coverage between head and its parent.
Looked throught= about 10 commits, didn't find differential code coverage and therefore no flakes}
\todo{Deflaker requires maven build. Randoop is on gradle.}
